\documentclass[a4paper,12pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{xcolor}

\title{Musik-AG der Hufelandstraße 16}
\subtitle{im 4. OG des Hinterhauses}
\author{}
\date{}

\pagenumbering{gobble}
\captionsetup{labelformat=empty}

\begin{document}

\maketitle

Wer Lust hat gemeinsam ein bisschen Musik zu machen kann sich gerne bei mir (Felix Springer) oder
auch anderen Mitgliedern der Musik-AG melden.

Im Musikraum haben wir ein Klavier, ein Schlagzeug, eine Akustikgitarre, einen Schellenring, Bongos
und Rasseln.
Gegen 10 Euro Pfand werden auch Schlüssel an die Mitglieder der AG verliehen.

Außerdem versuchen wir zu den größeren Feiern der Pinten-AG Konzerte zu organisieren.

{
    \color{orange}
    If you enjoy making music you should consider hitting up me (Felix Springer) or other members
    of the music group.

    In the music room we have a piano, a drum set, an acoustic guitar, a tambourine, bongo drums
    and maracas.
    The room is located on the fourth floor in the stairwell of the rear building.
    In exchange for a 10 Euro deposit members of the group can gain access to the room
    with keys.

    We are also focussing on giving concerts at the larger events of the Pinten-AG.
}

\noindent\rule{\textwidth}{1pt}

\vspace{20mm}

\begin{table}[h]
    \centering
    \caption{\large{Mitgliederliste {\color{orange} (member list)}}}
    \begin{tabular}{r|l}
        & Raum \color{orange}{(room)} \\
        \midrule
        Katharina Weißenborn & 163 \\
        Ryan Joseph George & 354 \\
        Carl Ole Janetzko & 462 \\
        Christian Reinprecht & 303 \\
        Felix Springer & 117 \\
    \end{tabular}
\end{table}



\end{document}
